\input{minutes.sty}

\begin{document}

\section*{424 W 49st Annual Meeting 2018 Minutes}

\textit{Aug 2nd 2018, 6 PM at the offices of Safeguard Realty. Dial in provided by 
Safeguard.}

\subsubsection*{Attended}

\begin{itemize}
\item Linda Carroll \& Bill Riley (3A + Comm).  Serving Treasurer/Secretary \& President 
respectively. Accompanied by Kenneth R Jacobs from “Spolzino, Smith Buss \& Jacobs LLP” legal 
firm.

\item Nicolas Dimov (3A).  Dialed In.

\item Daniel Chalk (4A).  Serving Vice President.

\item Gary Perlman (4B)

\item Manu Cornet (5A).  Dialed In.

\item Travis Hime (6A)

\item Ivan Villarruel and Ryan Villarruel (Safeguard Realty, Management)

\end{itemize}

\subsubsection*{Absent}

\begin{itemize}
\item Sheridan Vichie (5B) - Unrepresented.
\item Mida Chu (6B) - Proxy given to Daniel Chalk to vote for new board (only).
\end{itemize}

\subsection*{Items Discussed}

\begin{itemize}

\item Minor maintenance / Sanitation files / New Super.

\item Proposed Intercom/Security Camera upgrade.  Light discussion, ongoing.

\item Settlement of a Workmans Comp fine from the City relating to non-payment in 
2003.  A lawyer was hired by Safeguard on behalf of the building to try get this 
large (\${}10k), old, and previously unreported fine dismissed.  Unfortunately 
the 
best the lawyer could get for the building was a settlement at about half the 
original fine.  Going forward the buildings Super is now employed by Safeguard 
not 424 W49st so it should not be possible for us to violate again. 

\item Repairs needed to broken skylight glass in Commercial unit.  A dispute continues 
on whether this is the building or the Commercial units responsibility.  The 
dispute centers on what constitutes ‘a window’.  To be discussed further outside 
the AGM.

\item Relating to a dispute over Commercial/Residential heat payments and 
responsibilities Linda Carroll (for the Commercial Unit) provided excerpts from 
the Offering Plan (4th Amendment) arguing the case that the entire building is 
responsible for the Commercial heating bills (currently paid by the Commercial 
unit only).   Linda further provided a breakdown of the heating bill amounts 
paid from Jan 2013 to present.  Provided excerpts to be examined by the new 
board outside of the AGM.

\item Monthly Management Reports are now to be sent to all Owners not just the Board.
Reiteration of need for the building to establish a relationship with a legal 
firm to take advice on disputes.  “Spolzino, Smith Buss \& Jacobs LLP” has long 
been considered a good candidate for this, though they have consulted with Linda 
Carroll \& Bill Riley on a couple of items privately and so may not be able to 
fully represent the building on all matters (further discussion need with them 
to clarify appropriateness).

\item Common charges / Budget most likely need to be raised, however it was agreed 
that the new board would take some time to review the current financials and 
come back with proposals and any necessary assessments at a later date.  Minor 
repairs to resolve a leak in the 6A roof/facade area have so far been 
unsuccessful.  A new roof surface (with a quote of \$10,600) has been proposed 
by KNJ Contracting Inc. as their recommended next step.  Safeguard will review 
whether they can find any better quotes/alternatives and get back to us.

\item A new NYC Smoking Policy law (Local Law 147) will come into effect on Aug 28th 
2018.  424 will need some kind of By-Law / building policy update to ensure we 
are compliant.  “Spolzino, Smith Buss \& Jacobs LLP” suggested they are well 
placed to help with this and so may be consulted.

\item Elevator code changes are expected to take effect next year and 424 is not 
currently compliant.  Previous attempts have been made to get Midtown Elevator 
to provide us a with a proposal however that is still outstanding and needs to 
be chased with increasing urgency.  Based on the latest conversation with them 
we may need a whole new elevator computer as our is extremely old and any 
patches to it will be short term gains that will hurt us when the next code 
change comes along.  We need to get this budgeted for.

\item Possible addition of “No Bicycles” sign to facade fence.  Undecided if we will 
proceed, everyone shares the concern about fence damage from locks and 
obstruction of walkway but several Owners are not convinced the signs will be 
obeyed and so would merely be an eyesore.  Discussion can continue.

\item Several unit owners / tenants have made complaints about the surveillance 
cameras hung out of the commercial units front window and placed on the 3B 
terrace facing back at the rear facade / apartment windows.  A request has been 
made for the relevant parties to remove them.
\end{itemize}

\subsection*{New Board Election}

Only 3 people put their names forward for election and all votes cast were in 
support of them. The new board is therefore made up of Daniel Chalk, Travis Hime and Emmanuel 
Cornet. They will establish their specific roles outside of the AGM.

\subsection*{Follow-up Items}

\begin{itemize}
\item Get 424 compliant with the upcoming NYC Smoking Policy law by Aug 28th 2018.
Establish ongoing legal consultation for the building to help resolve disputes / 
law changes.

\item Share the Monthly Management Reports for an appropriate period of time with all 
Owners for transparency.  Management will share all new reports with all Owners 
going forward.

\item New board to review building financials and come back with proposals for common 
charge increases and any required assessments, ideally within 30 days.  
The board will start to build out a 10 year maintenance plan.

\item Review suggestion to establish a new bank account for the building to hold a 
reserve fund of at least 10\% of the operating budget (or the minimum typically 
required by mortgage providers), separate and distinct from the buildings 
day-to-day current account.

\item Resolve backlog of various maintenance items including facade repair (front and 
back), painting, deep clean of hallway flooring.  

\item Get a proposal for Elevator code change compliance from Midtown Elevator.
Work to close out Intercom / Security Camera project.
Continue to work to resolve leak in 6A roof.

\item Resolve dispute over repairs for skylight in the Commercial unit. 

\item Resolve dispute over Commercial/Residential heating payments.

\item Work with Safeguard to clarify / clear any outstanding violations held against 
the building.

\item Start to accumulate suggestions for amendments to our aging By-Laws (a medium 
term project).
\end{itemize}


\end{document}
