\input{../base.sty}

\begin{document}

\thispagestyle{empty}
\vspace*{\stretch{3}}

\begin{center}
\section*{{\huge 424 West 49$^{\textrm{\small th}}$ St Common Charges Payment}}
\end{center}

\vspace*{\stretch{3}}

The By Laws governing 424 West 49th Street Condominium (424) require the 424 board to
oversee the collection of common charges from each unit and to levy late payment charges
against them should they fail to pay by the required date. This document hereby establishes the
policy that will be used to perform that duty.

\vspace{1cm}

\begin{itemize}

\item To each unit corresponds its current balance for the payment of common
charges. A negative balance means that the unit owes the corresponding amount.

\item The common charges for each month are due on the first day of that month.
Therefore, the corresponding amount is deducted from each unit's balance on that
day.

%\item On the 10$^{\textrm{\small th}}$ day of the month, one of the board
%members will send, whenever possible, an email to the address registered for
%each corresponding unit, letting the owner know what their current balance is
%to the best of the board's knowledge as of that day.
%This recurring email is provided solely for convenience purposes and is not
%a contractual obligation for the board.

\item On the 20$^{\textrm{\small th}}$ day of the month, each unit's current
balance will be updated as follows:

\begin{itemize}

\item If the amount is equal to or higher than $-$\$$500$ (minus five hundred dollars), no
change will be made to the balance.

\item If the amount is lower than $-$\$$500$, late charges will be deducted from
the balance. The late charge amount is defined as \$$200$ (two hundred dollars)
or 10\% of the absolute value of the current balance, whichever is higher.

\end{itemize}

\item Should a unit be charged late charges for any period of time the board
reserves the right to additionally charge the unit any amounts spent by 424
on legal fees, etc., to recover the due amount.

\end{itemize}

\vspace{\stretch{3}}

\end{document}
