\input{../base.sty}

\begin{document}

\thispagestyle{empty}
\vspace*{\stretch{3}}

\begin{center}
\section*{{\huge 424 West 49$^{\textrm{\small th}}$ Street Smoking Policy}}
\end{center}

\vspace*{\stretch{3}}

In accordance with Section 17-502 of the NYC Administrative Code, 424 West 49th Street has adopted the following policy with respect to smoking on the property:

\vspace{1cm}

\begin{enumerate}

\item The term ‘smoking’ used in this policy is defined as inhaling, exhaling, breathing, burning or carrying a lighted cigarette, cigar, pipe (including a hookah pipe) or any other lighted or heated tobacco or legal plant product, or using a similar type of lighted, smoldering or vapor-producing product in any manner or form.  It further extends to the burning of incense sticks or similar that whilst not inhaled do produce smoke or odor.

\item No smoking is permitted in any of the indoor common areas including (but not limited to) the hallways, stairs, elevator, lobby or basement. 

\item No smoking is permitted on the building’s entrance steps or in anywhere inside the gated area at the front of the building.

\item Smoking is permitted within individual dwelling units and on roof decks and balconies, however, it is the owner’s responsibility to ensure that neither smoke nor the associated odor leak into any common areas or any other apartments from their own.  Leakage as described will be considered equal to smoking in the common areas. 

\item All unit owners must incorporate this policy into any lease or sale contract that they sign.  Failure to do so will be considered a violation of this policy and subject to the same fines.

\item All unit owners are responsible for violations of this policy (and payment of any associated fines) by their guests, tenants, hired workers, or anyone else that they have permitted to enter their property.  

\item Violators of this policy will be fined \$200 for the first offense, \$500 for the second offence, and \$1000 for every subsequent offence.

\item The board reserves the right to charge an identified violator for any costs incurred by the building to determine the offender or to enforce the policy.  This includes any professional services for testing, detection, or legal action.

\end{enumerate}

\vspace{\stretch{3}}

\end{document}
